\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\usepackage{listings}

\input{../Comments.text}
\input{../Common.text}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}








%%%%% 1 Plan %%%%%
\section*{Revision History}


\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
    Feb 8, 2026 & 1.0 & Initial draft \\
\bottomrule
\end{tabularx}
~\\


\newpage


\tableofcontents
% \listoftables
% \listoffigures


\newpage








%%%%% 2 Plan %%%%%
\section{Symbols, Abbreviations, and Acronyms}


Identical to the same section in SRS document \citep{SRS}.


\pagenumbering{arabic}


\newpage


This document presents the Verification and Validation (VnV) plan for \progname{}. It explains how the software and related artifacts will be reviewed, tested, and evaluated to provide confidence that the implemented pipeline satisfies its documented requirements and is suitable for its intended use.












%%%%% 2 General Information %%%%%
\section{General Information}




% 2.1 Summary
\subsection{Summary}


\progname{} aims to automate \href{https://mne.tools/stable/documentation/cookbook.html}{the typical M/EEG workflow}. Once the pipeline configuration is set up, user can simply call pipeline methods to execute analysis steps and access results without writing additional code. For example, user defines how to process raw data, events and epochs in the configuration, then it only takes a method call to get the resulting evoked data.




% 2.2 Objectives
\subsection{Objectives}


The primary objective of this Verification and Validation (VnV) plan is to build confidence in the correctness, reliability, and maintainability of the Eelbrain pipeline. In particular, this plan prioritizes:


\begin{itemize}
    \item \textbf{Functional correctness:} Ensuring that the implemented pipeline behaviour conforms to the functional requirements specified in the SRS.
    \item \textbf{Reliability:} Verifying that analyses produce consistent and structurally valid outputs for valid BIDS datasets.
    \item \textbf{Maintainability:} Ensuring that the implementation can accommodate likely future changes with reasonable effort.
\end{itemize}


\noindent The following objectives are considered out of scope for this VnV plan.


\begin{itemize}
    \item \textbf{Verification of external libraries (e.g., MNE-Python):} These tools are assumed to have been independently verified by their respective development teams.
    \item \textbf{Formal mathematical verification of analysis algorithms:} The project focuses on workflow integration rather than re-validating established neuroimaging algorithms.
    \item \textbf{Extensive user studies:} Due to limited resources and time constraints, only limited usability feedback will be collected.
\end{itemize}


These scope decisions reflect practical constraints in time and resources, and allow the VnV effort to focus on aspects of the system that are directly implemented and controlled within this project.




% 2.3 Extras
\subsection{Extras}


\begin{itemize}
    \item User manual: Provides installation steps, and small example workflows to help new users set up the environment, run the Eelbrain pipeline on sample BIDS data.
    \item Code walkthrough: Describes the main modules, data flow, and key methods in the pipeline to find potential issues. The walkthrough will focus on the end-to-end execution path from BIDS input parsing to result generation, including configuration loading, preprocessing orchestration, and output writing. During this process, reviewers will explicitly check requirement traceability, error-handling branches, and assumptions at module boundaries, and document identified risks and follow-up actions as GitHub issues.
\end{itemize}


% 2.4 Relevant Documentation
\subsection{Relevant Documentation}


\begin{itemize}
    \item Software Requirements Specification \citep{SRS}
    \item Module Guide \citep{MG}
    \item Module Interface Specification \citep{MIS}
\end{itemize}









%%%%% 3 Plan %%%%%
\section{Plan}


This section outlines the overall Verification and Validation (VnV) strategy for the project. It first defines the VnV team and their responsibilities, followed by the verification approach for the SRS, design documents, and the VnV plan itself. The implementation verification strategy and automated testing tools are then described.


% 3.1 Verification and Validation Team
\subsection{Verification and Validation Team}


\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule 
    \textbf{Member} & \textbf{Role} & \textbf{Responsibilities} \\
\midrule
    Zhangwenchi Li & Developer & Produce the VnV Plan and refine based on feedback \\
    Dr. Spencer Smith & Course Instructor & Provides feedback on engineering principles \\
    Dr. Christian Brodbeck & Domain Expert & Provides domain-specific information on requirements and validation \\
    Xiao Shao & Reviewer & Provides feedback on VnV plan \\
\bottomrule
\end{tabularx}




% 3.2 SRS Verification
\subsection{SRS Verification}


\begin{itemize}
    \item \textbf{Peer Review.} A classmate will review the SRS in detail using the course \href{https://zhangwenchili.github.io/CAS741-EelbrainPipeline/Checklists/SRS-Checklist.pdf}{SRS checklist} and make comments by creating issues in the \href{https://github.com/zhangwenchili/CAS741-EelbrainPipeline}{project repository}. The SRS will be revised to address each issue, and issues will only be closed after confirmation by the original reviewer.
    \item \textbf{Supervisor Review.} A structured walkthrough meeting will be scheduled with the supervisor. Prior to the meeting, a short summary and a prioritized checklist (e.g., goals, instance models, key requirements) will be shared to focus the discussion.

    During the meeting, the author will guide the review by highlighting critical sections and asking targeted, open-ended questions (e.g., about assumptions, clarity, and completeness), rather than going through the document line-by-line. Key feedback and open issues will be recorded.
    
    After the meeting, identified issues will be categorized (e.g., clarification, refinement, missing requirements) and addressed in the SRS, with follow-up questions resolved asynchronously if needed.
\end{itemize}



% 3.3 Design Verification
\subsection{Design Verification}


A classmate will review the MG and MIS document in detail using corresponding checklists (\href{https://zhangwenchili.github.io/CAS741-EelbrainPipeline/Checklists/MG-Checklist.pdf}{MG checklist} and \href{https://zhangwenchili.github.io/CAS741-EelbrainPipeline/Checklists/MIS-Checklist.pdf}{MIS checklist}) in course repo and make comments by creating issues in the project repository.




% 3.4 Verification and Validation Plan Verification
\subsection{Verification and Validation Plan Verification}


\begin{itemize}
    \item \textbf{Peer Review with Checklist.} A classmate will review the VnV Plan in detail using the course \href{https://zhangwenchili.github.io/CAS741-EelbrainPipeline/Checklists/VnV-Checklist.pdf}{VnV checklist} and create review comments as issues in the project repository. The review will focus on correctness, consistency with the SRS and design documents, and completeness of planned verification activities.
    \item \textbf{Walkthrough and Scope Check.} A short walkthrough session will be held to explain the rationale behind selected test strategies, priorities, and scope boundaries (including what is explicitly out of scope). This helps ensure that the planned VnV activities are realistic and aligned with project constraints.
    \item \textbf{Issue Resolution and Exit Criteria.} Reported issues will be categorized (e.g., ambiguity, missing coverage, inconsistency, or feasibility concern), addressed in the VnV Plan, and linked to corresponding revisions. The section will be considered verified only after all high-priority issues are resolved and the reviewer confirms closure.
\end{itemize}




% 3.5 Implementation Verification
\subsection{Implementation Verification}


Unit testing planned in \autoref{unit_test_description} will be developed as the major method for implementation verification. A code walkthrough will be performed to inspect the most critical modules.




% 3.6 Automated Testing and Verification Tools
\subsection{Automated Testing and Verification Tools}


\begin{itemize}
    \item \textbf{GitHub Actions}: Automates CI/CD workflows to run tests, checks, and deployments on every push or pull request.
    \item \textbf{pytest}: A Python testing framework used to write and execute unit and integration tests efficiently. The written tests will be integrated and executed in GitHub Actions.
    \item \textbf{flake8}: A linting tool that checks Python code for style issues, syntax errors, and adherence to coding standards.
    \item \textbf{Codecov}: A code coverage reporting tool that measures how much of the codebase is tested and produces coverage reports.
\end{itemize}




% 3.7 Software Validation
\subsection{Software Validation}


Out of scope for this project.












%%%%% 4 System Tests %%%%%
\section{System Tests}


This section defines the system-level tests derived from the Software Requirements Specification (SRS). It first presents test cases for functional requirements, followed by tests addressing nonfunctional requirements such as usability, maintainability, and portability. Finally, a traceability matrix is provided to explicitly link requirements to their corresponding test cases. All system tests will use the \href{https://mne.tools/stable/documentation/datasets.html#sample}{MNE sample dataset} as input data.



% 4.1 Tests for Functional Requirements
\subsection{Tests for Functional Requirements}


The following system-level test cases are derived from the functional requirements (R1--R5) identified in the SRS. For each functional requirement, at least one corresponding test case (FR-01--FR-04) is defined, specifying initial state, inputs, expected outputs, and pass/fail criteria. This ensures that the implemented Eelbrain pipeline behaviour can be systematically checked against the required functionality, and that there is clear traceability from the SRS requirements to the verification activities.

		
\paragraph{BIDS Path Templating}


\begin{enumerate}


\item{FR-01\\}
    Control: Automatic \\
    Initial State: Eelbrain pipeline is initialized. \\
    Input:
        \begin{itemize}
            \item \href{https://mne.tools/stable/documentation/datasets.html#sample}{MNE sample dataset} containing multiple file paths;
            \item Methods calls on pipeline to access file paths and load files.
        \end{itemize}
    Output: Eelbrain pipeline successfully loads all correct file paths or handles incorrect ones with informative errors. \\
    Test Case Derivation: From MNE sample data. \\
    How test will be performed: Call pipeline methods to get paths or load files. Assertions will check that
        \begin{itemize}
            \item All file paths are correctly constructed from file templates in the valid case;
            \item All files are successfully discovered in the valid case;
            \item An appropriate exception or error message is raised in the invalid case, explicitly identifying missing files.
        \end{itemize}


\end{enumerate}


\begin{tabularx}{\textwidth}{p{2cm}p{2cm}p{4.5cm}X}
\toprule 
    \textbf{Test Case ID} & \textbf{File Type} & \textbf{Path Invoked} & \textbf{Expected Behaviour} \\
\midrule
    FR-01-1 & Raw MEG data & sub-01/ses-01/meg/ sub-01\_ses-01\_task-auditory\_meg.fif & Pipeline method returns a loaded MNE Raw object with correct subject, session and task information. \\

    FR-01-2 & Raw MEG data & sub-01/meg/sub-01\_task-auditory\_meg.fif & Pipeline raises FileNotFoundError with full expected path. \\

    FR-01-3 & Channels file & sub-01/ses-01/meg/sub-01\_ses-01\_task-auditory\_channels.tsv & Pipeline method can read channels file correctly, returning an empty bad channels list. \\

    FR-01-4 & FreeSurfer MRI & {root}/derivatives/ freesurfer/sub-01/bem/outer\_skull.surf & Pipeline method returns the bem model. \\
\bottomrule
\end{tabularx}


\paragraph{Automatic parameter inference from dataset}


\begin{enumerate}


\item{FR-02\\}
    Control: Automatic \\
    Initial State: Eelbrain pipeline is initialized. \\
    Input: 
        \begin{itemize}
            \item A fake dataset with multiple subjects, sessions and tasks created by duplicating \href{https://mne.tools/stable/documentation/datasets.html#sample}{MNE sample dataset};
            \item A minimal pipeline configuration file with BIDS entities omitted (e.g., subject/session/task). An example configuration file can be found \href{https://github.com/Eelbrain/Eelbrain/blob/main/examples/imagenet/imagenet.py}{here}.
        \end{itemize}
    Output: BIDS entities are properly inferred from the dataset. \\
    Test Case Derivation: From MNE sample data. \\
    How test will be performed: Access pipeline attributes related to BIDS entities. Assertions will check that inferred values are identical to the correct BIDS entities.


\end{enumerate}


\begin{tabularx}{\textwidth}{p{2cm}p{2cm}p{4.5cm}X}
\toprule 
    \textbf{Test Case ID} & \textbf{BIDS Entity} & \textbf{Example Dataset Structure} & \textbf{Expected Inferred Value / Behaviour} \\
\midrule
    FR-02-1 & Subject & Dataset contains sub-01, sub-02, sub-03 directories & The pipeline subjects list is \texttt{["01", "02", "03"]} \\

    FR-02-2 & Session & Dataset contains ses-01, ses-02 directories under each subject directory & The pipeline sessions list is \texttt{["01", "02"]} \\

    FR-02-3 & Task & Dataset contains task-sample1, task-sample2 directories under each session directory & The pipeline tasks list is \texttt{["sample1", "sample2"]}. \\
\bottomrule
\end{tabularx}


\paragraph{Support for sensor-space analysis}


\begin{enumerate}


\item{FR-03\\}
    Control: Automatic \\
    Initial State: Eelbrain pipeline initialized. \\
    Input:
        \begin{itemize}
            \item sub-01\_task-auditory\_meg.fif in MNE sample dataset;
            \item A pipeline configuration includes sensor-space processing parameters (preprocessing steps, epoch definitions, etc.);
            \item Methods calls on pipeline to execute sensor-space analysis steps and load processed data.
        \end{itemize}
    Output: The pipeline successfully processes sensor-space data with correct dimensions. \\
    Test Case Derivation: The MNE sample data provides the expected dimensions and properties of sensor-space data. \\
    How test will be performed: Assertions will check that
    \begin{itemize}
        \item The returned sensor-space data are in correct MNE-Python data structures (e.g., Epochs objects);
        \item The dimensions of processed sensor-space data match expected values (the number of channels, time points, or epochs).
    \end{itemize}
    


\end{enumerate}


\begin{tabularx}{\textwidth}{p{2.5cm}p{5cm}X}
\toprule 
    \textbf{Test Case ID} & \textbf{Processing Stage} & \textbf{Anticipated Result} \\
\midrule

    FR-03-1 & Maxwell filtering & Returned raw object maintains 376 channels and 600.614 Hz sampling rate. No NaN or infinite values in data array. \\

    FR-03-2 & Epochs extraction & Epochs object with shape (280--300 epochs, 376 channels, 421 time points). Epoch rejection rate less than 15\%. \\

    FR-03-3 & Evoked response computation & Evoked object averaged across trials with shape (376 channels, 421 time points). Peak amplitude 250--350 fT for auditory sensors (channels MEG14xx). \\
\bottomrule
\end{tabularx}


\paragraph{Support for source-space analysis}


\begin{enumerate}


\item{FR-04\\}
    Control: Automatic \\
    Initial State: Eelbrain pipeline initialized and sensor-space processing completed. \\
    Input:
        \begin{itemize}
            \item \href{https://mne.tools/stable/documentation/datasets.html#sample}{MNE sample dataset};
            \item Methods calls on pipeline to execute source-space analysis steps and load STC (source time course) data.
        \end{itemize}
    Output: The pipeline successfully computes source-space data with correct properties. The returned source-space data has a shape of 7498 vertices and 421 time points; its peak amplitude in right auditory cortex is 15--25 dSPM units. \\
    Test Case Derivation: The MNE sample data provides the expected dimensions and properties of source-space data. \\
    How test will be performed: Run the source localization workflow. Assertions will check that 
    \begin{itemize}
        \item The returned source-space data is in an MNE-Python SourceEstimate object;
        \item The returned source-space data has a shape of 7498 vertices and 421 time points; its peak amplitude in right auditory cortex is 15--25 dSPM units.
    \end{itemize}
    


\end{enumerate}




% 4.2 Tests for Nonfunctional Requirements
\subsection{Tests for Nonfunctional Requirements}





\subsubsection{Usability}


\paragraph{Usability survey acceptance test}


\begin{enumerate}


\item{NFR-01\\}
    Type: Manual \\
    Initial State: An alpha version of Eelbrain pipeline is available; a user group consisting of neuroscience researchers is selected. \\
    Input/Condition: Participants complete a short analysis task (load raw files, compute evoked response and access results) and then complete a usability survey questionnaire (\ref{sec_usability_survey_questionnaire}). \\
    Output/Result: At least 80\% of respondents rate the software as easy to use. \\
    How test will be performed: Collect questionnaire results; compute the percentage of "easy to use" responses and verify if it is larger than 80\%.


\end{enumerate}




\subsubsection{Maintainability}


\paragraph{Likely-change effort threshold test}


\begin{enumerate}


\item{NFR-02\\}
    Type: Dynamic, Manual \\
    Initial State: Baseline development time is recorded for the original implementation; codebase is under version control. \\
    Input/Condition: Select one likely change (e.g., adding support for one more BIDS entity or one more preprocessing operation) and implement it by a developer with relevant domain knowledge. \\
    Output/Result: The measured effort to implement the chosen likely change is less than 0.5 of the original development time. \\
    How test will be performed: Track engineering time using commits; compare total effort against the recorded baseline and confirm it satisfies the threshold.


\end{enumerate}


\subsubsection{Portability}


\paragraph{Cross-platform installation and execution test}


\begin{enumerate}


\item{NFR-03\\}
    Type: Manual \\		
    Initial State: Clean Windows, macOS, and Linux environments prepared. \\
    Input/Condition: Install Eelbrain pipeline and run developed pytest scripts on each OS using the MNE sample dataset. \\
    Output/Result: The pipeline installs and runs successfully on Windows, macOS, and Linux with consistent results for the workflow. \\
    How test will be performed: Create different workflows for each OS on Github Actions.


\end{enumerate}




% 4.3 Traceability Between Test Cases and Requirements
\subsection{Traceability Between Test Cases and Requirements}


\begin{table}[h]
\centering
\begin{tabularx}{0.6\textwidth}{p{3cm}X}
\toprule
    \textbf{Requirements} & \textbf{Test Cases} \\
\midrule
    R1 & FR-01 \\
    R2 & FR-02 \\
    R3 & FR-03, FR-05 \\
    R4 & FR-04, FR-05 \\
    NFR1 & NFR-01 \\
    NFR2 & NFR-02 \\
    NFR3 & NFR-03 \\
\bottomrule
\end{tabularx}
\end{table}




\newpage








%%%%% 5 Unit Test Description %%%%%
\section{Unit Test Description} \label{unit_test_description}




% 5.1 Unit Testing Scope
\subsection{Unit Testing Scope}


% scope, priority
\noindent Unit testing focuses on leaf modules implemented in \progname{} and specified in MIS \citep{MIS} and MG \citep{MG}: Pipeline (M1), TreeModel (M2), FileTree (M3), Preprocessing (M4), Epoch (M5), and Covariance (M6). Since MNE-Python (M7) is an external dependency, unit tests will verify integration contracts (input/output types and exception propagation) at module boundaries rather than re-testing MNE-Python internals.

\begin{itemize}
    \item \textbf{In scope:} exported access routines and key state transitions defined in MIS.
    \item \textbf{Out of scope:} numerical correctness proofs of third-party algorithms and full end-to-end workflow behaviour (covered by system tests in Section 4).
    \item \textbf{Priority:} M2--M4 are highest priority because they encapsulate path templating, field validation, and preprocessing orchestration that are frequently reused by M1.
\end{itemize}



% 5.2 Tests for Functional Requirements
\subsection{Tests for Functional Requirements}




\subsubsection{Pipeline Module (M1)}

\begin{enumerate}

\item{UT-M1-01\\}
    Type: Automatic \\
    Initial State: A pipeline instance is created with valid test dataset root. \\
    Input: A valid raw-file path generated by FileTree module. \\
    Output: \lstinline|load_raw| returns an \lstinline|mne.io.Raw| object. \\
    Test Case Derivation: From MIS M1 exported routine \lstinline|load_raw| and its output contract. \\
    How test will be performed: Use pytest with a temporary dataset fixture; call \lstinline|load_raw| and assert returned object type and non-empty info fields.

\item{UT-M1-02\\}
    Type: Automatic \\
    Initial State: A pipeline instance is created with a path to a non-existent raw file. \\
    Input: A missing raw-file path. \\
    Output: \lstinline|FileNotFoundError| is raised by \lstinline|load_raw|. \\
    Test Case Derivation: From MIS M1 exception rule for \lstinline|load_raw|. \\
    How test will be performed: Mock/prepare an invalid path and assert \lstinline|pytest.raises(FileNotFoundError)|.

\item{UT-M1-03\\}
    Type: Automatic \\
    Initial State: Valid raw data and epoch definitions are available. \\
    Input: Calls to \lstinline|load_events| and \lstinline|load_epochs|. \\
    Output: Events and epochs objects are returned as \lstinline|mne.events.Events| and \lstinline|mne.Epochs| objects respectively. \\
    Test Case Derivation: From MIS M1 access routine semantics for \lstinline|load_events| and \lstinline|load_epochs|. \\
    How test will be performed: Call routines using test fixtures and assert object types; verify runtime error path when no valid events exist.

\end{enumerate}

\subsubsection{TreeModel Module (M2)}
\begin{enumerate}

\item{UT-M2-01\\}
    Type: Automatic \\
    Initial State: A new TreeModel object is created. \\
    Input: \lstinline|_register_field(field, values, default)| with valid values and default; retrieve the value through \lstinline|get|. \\
    Output: Field is registered and the value is retrieved correctly. \\
    Test Case Derivation: From MIS M2 state transition of \lstinline|_register_field| and output of \lstinline|get|. \\
    How test will be performed: Register a field, assert internal dictionaries are updated, and verify \lstinline|get(field)| equals default value.

\item{UT-M2-02\\}
    Type: Automatic \\
    Initial State: A TreeModel object exists with one registered field. \\
    Input: Re-register same field name; set value outside allowed domain. \\
    Output: \lstinline|ValueError| is raised. \\
    Test Case Derivation: From MIS M2 exception semantics of \lstinline|_register_field| and \lstinline|set|. \\
    How test will be performed: Invoke invalid operations and assert \lstinline|pytest.raises(ValueError)|.

\item{UT-M2-03\\}
    Type: Automatic \\
    Initial State: Multiple fields with finite value sets are registered. \\
    Input: \lstinline|iter(field_names)|. \\
    Output: Iterator yields Cartesian combinations of field values. \\
    Test Case Derivation: From MIS M2 output semantics of \lstinline|iter|. \\
    How test will be performed: Materialize iterator to list and compare against expected combination count and representative tuples.

\end{enumerate}

\subsubsection{FileTree Module (M3)}

\begin{enumerate}

\item{UT-M3-01\\}
    Type: Automatic \\
    Initial State: A FileTree object is created with valid root directory. \\
    Input: \lstinline|get(field_name, mkdir=False)| for an existing path template. \\
    Output: Expanded \lstinline|pathlib.Path| object is returned. \\
    Test Case Derivation: From MIS M3 output contract of \lstinline|get|. \\
    How test will be performed: Register path fields via inherited interface and assert path expansion matches expected filesystem location.

\item{UT-M3-02\\}
    Type: Automatic \\
    Initial State: FileTree root directory is intentionally missing. \\
    Input: \lstinline|get(field_name, mkdir=True)|. \\
    Output: \lstinline|OSError| is raised. \\
    Test Case Derivation: From MIS M3 exception semantics of \lstinline|get|. \\
    How test will be performed: Use temporary directory fixture, remove root, call \lstinline|get| with mkdir, assert exception.

\item{UT-M3-03\\}
    Type: Automatic \\
    Initial State: Test directory contains files matching and not matching a pattern. \\
    Input: \lstinline|glob(pattern)|. \\
    Output: Only matching paths are returned. \\
    Test Case Derivation: From MIS M3 output semantics of \lstinline|glob|. \\
    How test will be performed: Create controlled files in temp directory and compare returned file set to expected matches.

\end{enumerate}

\subsubsection{Preprocessing Module (M4)}

\begin{enumerate}

\item{UT-M4-01\\}
    Type: Automatic \\
    Initial State: Preprocessing object has valid \lstinline|mne_bids.BIDSPath| input. \\
    Input: \lstinline|load(bids_path)|. \\
    Output: \lstinline|mne.io.Raw| object is returned. \\
    Test Case Derivation: From MIS M4 output contract of \lstinline|load|. \\
    How test will be performed: Mock underlying read when needed and assert returned type plus correct call arguments.

\item{UT-M4-02\\}
    Type: Automatic \\
    Initial State: No corresponding raw file exists for given BIDS path. \\
    Input: \lstinline|load(bids_path)| with missing file. \\
    Output: \lstinline|FileNotFoundError| is raised. \\
    Test Case Derivation: From MIS M4 exception rule of \lstinline|load|. \\
    How test will be performed: Construct missing path in fixture and assert exception.

\item{UT-M4-03\\}
    Type: Automatic \\
    Initial State: Valid raw object is available for ICA creation. \\
    Input: \lstinline|make_ica| then \lstinline|load_ica|. \\
    Output: ICA cache is created and loaded as \lstinline|mne.preprocessing.ICA| object. \\
    Test Case Derivation: From MIS M4 transitions and outputs for ICA routines. \\
    How test will be performed: Use temporary cache directory, run creation/loading path, and assert output type or expected runtime/file exceptions.

\end{enumerate}

\subsubsection{Epoch Module (M5) and Covariance Module (M6)}

\begin{enumerate}

\item{UT-M5-01\\}
    Type: Automatic \\
    Initial State: Epoch definition object is instantiated. \\
    Input: Configuration constants (\lstinline|task|, \lstinline|sel|, \lstinline|tmin|, \lstinline|tmax|, \lstinline|samplingrate|). \\
    Output: Values can be accessed by M1 and printed to console. \\
    Test Case Derivation: From MIS M5 exported constants contract. \\
    How test will be performed: Instantiate object with valid and invalid sampling settings; assert values and validation behaviour.

\item{UT-M6-01\\}
    Type: Automatic \\
    Initial State: Valid epochs object exists for covariance estimation. \\
    Input: \lstinline|make()| with supported method values ("empirical", "best", "ad\_hoc"). \\
    Output: \lstinline|mne.cov.Covariance| object is produced. \\
    Test Case Derivation: From MIS M6 output semantics of \lstinline|make|. \\
    How test will be performed: Call routine on test epochs and assert return type and matrix dimensional consistency.

\item{UT-M6-02\\}
    Type: Automatic \\
    Initial State: Valid epochs object exists for covariance estimation. \\
    Input: \lstinline|make()| with unsupported method values (e.g., "random"). \\
    Output: \lstinline|RuntimeError| is raised. \\
    Test Case Derivation: From MIS M6 exception semantics of \lstinline|make|. \\
    How test will be performed: Inject failing input conditions and assert runtime exception propagation.
\end{enumerate}




% 5.3 Tests for Nonfunctional Requirements
\subsection{Tests for Nonfunctional Requirements}

\begin{enumerate}

\item{UT-NFR-01 (Maintainability-Oriented Unit Test Quality)\\}
    Type: Automatic \\
    Initial State: Unit test suite is implemented in pytest and connected to CI. \\
    Input/Condition: Run unit tests with coverage collection on each pull request. \\
    Output/Result: Statement coverage for modules M1--M6 remains at or above 80\%. \\
    How test will be performed: Execute pytest with coverage plugin in GitHub Actions and enforce threshold as a CI gate.

\item{UT-NFR-02 (Portability-Oriented Unit Execution)\\}
    Type: Automatic \\
    Initial State: Same unit test suite and test fixtures are available on Linux, macOS, and Windows CI runners. \\
    Input/Condition: Execute unit tests in a matrix build across three operating systems. \\
    Output/Result: Core unit tests (M2--M4 at minimum) pass consistently across all target platforms. \\
    How test will be performed: Configure GitHub Actions OS matrix and compare pass/fail outcomes for each platform.

\end{enumerate}




% 5.4 Traceability Between Test Cases and Modules
\subsection{Traceability Between Test Cases and Modules}

\begin{table}[h]
\centering
\begin{tabularx}{0.9\textwidth}{p{2.2cm}X}
\toprule
    \textbf{Module} & \textbf{Unit Test Cases} \\
\midrule
    M1 (Pipeline) & UT-M1-01, UT-M1-02, UT-M1-03 \\
    M2 (TreeModel) & UT-M2-01, UT-M2-02, UT-M2-03 \\
    M3 (FileTree) & UT-M3-01, UT-M3-02, UT-M3-03 \\
    M4 (Preprocessing) & UT-M4-01, UT-M4-02, UT-M4-03 \\
    M5 (Epoch) & UT-M5-01 \\
    M6 (Covariance) & UT-M6-01, UT-M6-02 \\
    Cross-module NFR checks & UT-NFR-01, UT-NFR-02 \\
\bottomrule
\end{tabularx}
\caption{Traceability Between Unit Tests and Modules}
\end{table}
\newpage








\bibliographystyle{plainnat}
\bibliography{../../refs/References}




\newpage








\section{Appendix}


\subsection{Usability Survey Questionnaire}
 \label{sec_usability_survey_questionnaire}

Participants will answer the following questions after completing the representative tasks defined for usability evaluation. Unless otherwise noted, each item uses a 5-point Likert scale: 1 = Strongly Disagree, 2 = Disagree, 3 = Neutral, 4 = Agree, 5 = Strongly Agree.

\begin{enumerate}
    \item The installation and environment setup instructions were clear and easy to follow.
    \item I could understand how to prepare and organize input data for the pipeline.
    \item The command-line usage and required options were easy to understand.
    \item The error messages and warnings were clear enough to help me recover from mistakes.
    \item The generated outputs (files and logs) were easy to locate and interpret.
    \item The overall workflow felt efficient for completing the intended analysis tasks.
    \item The documentation was sufficient for me to complete tasks without external help.
    \item I feel confident that I could run the pipeline again on a different dataset.
\end{enumerate}

Open-ended questions:
\begin{enumerate}
    \item What was the most difficult step in the workflow, and why?
    \item Which part of the documentation should be improved first?
    \item What feature or improvement would most increase your confidence in using this pipeline?
\end{enumerate}








\end{document}